\LARGE The Bitcoin Lightning Network:\\ \Large Scalable Off-Chain Instant Payments

### 2015-07-24 paper.tex
Thanks to corrections from David Sterry (prior commit also incorporates typo/corrections on page 2,4,6,8,12,17,54 on the pdf ver 0.5.9)

For example, if a parent transaction is spent by a child with a nSequence value
of 10, if there have been 10 blocks and one of them has the

@@

	\item Micropayments. Bitcoin blockchain fees are far too high to accept
		micropayments, especially with the smallest of values. With this
		system, near-instant micropayments using Bitcoin without a 3rd
		party custodian would be possible. It would enable, for example,
		paying per-megative for internet service or per-article to read
		a newspaper.

>>>>

For example, if a parent transaction output is spent by a child with a nSequence
value of 10, one must wait 10 confirmations before the transaction becomes
valid. However, if the timestop flag has been set, the counting of confirmations
stops, even with new blocks. If 6 confirmations have elapsed (4 more are
necessary for the transaction to be valid), and the timestop block has been set
on the 7th block, that block does not count towards the nSequence requirement of
10 confirmations; the child is still at 6 blocks for the relative confirmation
value. Functionally, this will be stored as some kind of auxiliary timestop
block height which is used only for tracking the timestop value. When the
timestop bit is set, all transactions using an nSequence value will stop
counting until the timestop bit has been unset. This gives sufficient time and
block-space for transactions at the current auxiliary timestop block height to
enter into the blockchain, which can prevent systemic attackers from
successfully attacking the system.

@@

	\item Micropayments. Bitcoin blockchain fees are far too high to accept
		micropayments, especially with the smallest of values. With this
		system, near-instant micropayments using Bitcoin without a 3rd
		party custodian would be possible. It would enable, for example,
		paying per-megabyte for internet service or per-article to read
		a newspaper.
